Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-15 PAPER.tex
Variation due between EoR injection realization is not noise, its most like cosmic variance or something.
Slight elaboration in the Bayes intro

One issue to address is how one incorporates the randomness of $P_{\rm out}$ into our signal loss corrections. A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e. behaves like noise) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e. how much coupling there is, which affects how much loss results).

Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$. Bayes' rule gives

\begin{equation}
\label{eq:Bayes}
p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})}
  p(P_{\rm in}) ,
\end{equation}

>>>>

One issue to address is how one incorporates the randomness of $P_{\rm out}$ into our signal loss corrections. A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e. cosmic variance) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e. how much coupling there is, which affects how much loss results).

Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$.  Bayes' rule relates the posterior, which we don't know, to the reverse probability, which we do know, in other words,

\begin{equation}
\label{eq:Bayes}
p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})},
  p(P_{\rm in}) ,
\end{equation}
